---
title: "Telco Churn"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Updating Libraries
```{r echo=T, results='hide',message=FALSE,warning=FALSE}
library(rio)
library(formattable)
library(dplyr)
library(tidyverse)
library(readxl)
library(corrplot)
library(stargazer)
library(car)
library(PerformanceAnalytics)
library(tidyr)
library(tm)
library(MASS)
library(AER)
library(ggplot2)
library(lubridate)
library(lattice)
library(lme4)
library(MuMIn)
library("ggridges")
library("hrbrthemes")
library(ggthemes)
library("maps")
library("mapproj")
library(cowplot)
library(ROCR)

options(scipen = 999)
```

## Importing Data
```{r}
df<-read_xlsx("TelcoChurn.xlsx",sheet = "Data")
```

```{r}
str(df)
```
## Checking Nulls
```{r}
colSums(is.na(df))
```
## Dropping Nulls
```{r}
df<-na.omit(df)
```

## Converting to factor and releveling
```{r}
df$gender<-as.factor(df$gender)
df$SeniorCitizen<-as.factor(df$SeniorCitizen)
df$Partner<-as.factor(df$Partner)
df$Dependents<-as.factor(df$Dependents)
df$Contract<-as.factor(df$Contract)
df$PaperlessBilling<-as.factor(df$PaperlessBilling)
df$Churn <- ifelse(df$Churn=="Yes", 1, 0)
df$Churn<-as.factor(df$Churn)
```


## Making separate datasets for telephone only, Internet only and customers that use both services 
```{r}
Both<-subset(df, PhoneService=='Yes' & InternetService!='No')
Telephone<-subset(df, PhoneService=='Yes' & InternetService=='No')
Internet<-subset(df, PhoneService=='No' & InternetService!='No')
```

## Preparing data for customers that use both, Telephone and Internet Services
```{r}
unique(Both$PhoneService)
Both$MultipleLines<-as.factor(Both$MultipleLines)
Both$OnlineSecurity<-as.factor(Both$OnlineSecurity)
Both$OnlineBackup<-as.factor(Both$OnlineBackup)
Both$DeviceProtection<-as.factor(Both$DeviceProtection)
Both$TechSupport<-as.factor(Both$TechSupport)
Both$StreamingTV<-as.factor(Both$StreamingTV)
Both$StreamingMovies<-as.factor(Both$StreamingMovies)
Both$PaymentMethod<-as.factor(Both$PaymentMethod)
Both$InternetService<-as.factor(Both$InternetService)
Both$PhoneService<-NULL
summary(Both)
```


## Preparing data for Telephone Only Customers
```{r}
Telephone$MultipleLines<-as.factor(Telephone$MultipleLines)
Telephone$PaymentMethod<-as.factor(Telephone$PaymentMethod)

Telephone$PhoneService<-NULL
Telephone$OnlineSecurity<-NULL
Telephone$OnlineBackup<-NULL
Telephone$DeviceProtection<-NULL
Telephone$TechSupport<-NULL
Telephone$StreamingTV<-NULL
Telephone$StreamingMovies<-NULL
Telephone$InternetService<-NULL
summary(Telephone)
```

## Preparing data for Internet Only Customers
```{r}
Internet$PaymentMethod<-as.factor(Internet$PaymentMethod)
Internet$OnlineSecurity<-as.factor(Internet$OnlineSecurity)
Internet$OnlineBackup<-as.factor(Internet$OnlineBackup)
Internet$DeviceProtection<-as.factor(Internet$DeviceProtection)
Internet$TechSupport<-as.factor(Internet$TechSupport)
Internet$StreamingTV<-as.factor(Internet$StreamingTV)
Internet$StreamingMovies<-as.factor(Internet$StreamingMovies)



Internet$MultipleLines<-NULL
Internet$PhoneService<-NULL
Internet$InternetService<-NULL
summary(Internet)
```


```{r}
colSums(is.na(Internet))
```

```{r}
knitr::opts_chunk$set(echo = TRUE,fig.width = 12,fig.height = 20)
```

## Visualizing predictors with churn possibility - BOTH
```{r}
df2<-table(Both$Churn,Both$gender)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Gender")+ylab("Percentage")
a<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Both$Churn,Both$Partner)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Partner")+ylab("Percentage")
b<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Both$Churn,Both$Dependents)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Dependents")+ylab("Percentage")
c<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Both$Churn,Both$MultipleLines)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Multiple Lines")+ylab("Percentage")
d<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Both$Churn,Both$InternetService)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Internet Service")+ylab("Percentage")
e<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Both$Churn,Both$OnlineSecurity)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Online Security")+ylab("Percentage")
f<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Both$Churn,Both$OnlineBackup)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Online Backup")+ylab("Percentage")
g<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Both$Churn,Both$DeviceProtection)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Device Protection")+ylab("Percentage")
h<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Both$Churn,Both$TechSupport)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Tech Support")+ylab("Percentage")
i<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Both$Churn,Both$StreamingTV)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Streaming TV")+ylab("Percentage")
j<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Both$Churn,Both$StreamingMovies)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Streaming Movies")+ylab("Percentage")
k<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Both$Churn,Both$Contract)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Contract")+ylab("Percentage")
l<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Both$Churn,Both$PaperlessBilling)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Paperless Billing")+ylab("Percentage")
m<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Both$Churn,Both$SeniorCitizen)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)

p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Senior Citizen")+ylab("Percentage")
o<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Both$Churn,Both$PaymentMethod)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)

p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Payment Method")+ylab("Percentage")
n<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

cowplot::plot_grid(a, b,c,d,e,f,g,h,i,j,k,l,m,n,o,ncol = 3)
```
```{r}
knitr::opts_chunk$set(echo = TRUE,fig.width = 8,fig.height = 5.5)
```

```{r}
a<-Both %>%
  group_by(Churn) %>%
  ggplot()+
  geom_boxplot(aes(x=Churn,y=tenure,fill="coral"))+
  guides(fill=FALSE)

b<-Both %>%
  group_by(Churn) %>%
  ggplot()+
  geom_boxplot(aes(x=Churn,y=MonthlyCharges,fill="coral"))+
  guides(fill=FALSE)

c<-Both %>%
  group_by(Churn) %>%
  ggplot()+
  geom_boxplot(aes(x=Churn,y=TotalCharges,fill="coral"))+
  guides(fill=FALSE)

cowplot::plot_grid(a, b,c,ncol = 3)
```

```{r}
numerics=Both[c('tenure','MonthlyCharges','TotalCharges')]
correlations=cor(numerics)
d<-corrplot(correlations,method = "number",type="upper")
```

## Separating Data sets into training and test - BOTH
```{r}
set.seed(1024)
trainIndex <- sample(1:nrow(Both), size=round(0.75*nrow(Both)), replace=FALSE)
train <- Both[trainIndex,]
test  <- Both[-trainIndex,]
dim(train); dim(test)
summary(train)
```
## Creating the model - BOTH
```{r}
reg1  <- glm(Churn ~ SeniorCitizen+ Partner+ Dependents + MultipleLines + InternetService + OnlineSecurity + OnlineBackup + DeviceProtection + TechSupport + Contract + PaperlessBilling+PaymentMethod+tenure,family=binomial (link="logit"),data=train)
summary(reg1)
```

```{r}
vif(reg1)
dwtest(reg1)
```

## Calculating Accuracy, Precision, Recall and F-1 Score
```{r}
test_x <- test[ , c(1:19)]
predlogit <-predict(reg1, newdata=test_x, type="response")
predlogit <- ifelse(predlogit>0.24, 1, 0)

ConfusionMatrix<-table(test$Churn, predlogit)                         # Confusion matrix
ClassificationError <- mean(predlogit != test$Churn) # Classification error

pr <- prediction(predlogit, test$Churn)
prf <- performance(pr, measure="tpr", x.measure="fpr")
plot(prf)                                                 # ROC plot: TPR vs FPR

auc <- performance(pr, measure="auc")
auc <- auc@y.values[[1]]

TP = ConfusionMatrix[2,2]
TN = ConfusionMatrix[1,1]
FP = ConfusionMatrix[1,2]
FN = ConfusionMatrix[2,1]

precision<- round(TP / (TP + FP), 2)
recall<- round(TP / (TP + FN), 2)
f1_score<- round((2 * precision * recall) / (precision + recall), 2)
ConfusionMatrix
print(paste("Accuracy = ", 1-ClassificationError))
print(paste("AUC = ", auc))
print(paste("Precision = ", precision))
print(paste("Recall = ", recall))
print(paste("F-1 Score = ", f1_score))
```

```{r}
knitr::opts_chunk$set(echo = TRUE,fig.width = 12,fig.height = 15)
```

## Visualizing predictors with churn possibility - Telephone only
```{r}
df2<-table(Telephone$Churn,Telephone$gender)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Gender")+ylab("Percentage")
a<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Telephone$Churn,Telephone$Partner)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Partner")+ylab("Percentage")
b<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Telephone$Churn,Telephone$Dependents)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Dependents")+ylab("Percentage")
c<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Telephone$Churn,Telephone$MultipleLines)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Multiple Lines")+ylab("Percentage")
d<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Telephone$Churn,Telephone$SeniorCitizen)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Senior Citizen")+ylab("Percentage")
e<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))


df2<-table(Telephone$Churn,Telephone$Contract)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Contract")+ylab("Percentage")
f<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Telephone$Churn,Telephone$PaperlessBilling)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Paperless Billing")+ylab("Percentage")
g<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Telephone$Churn,Telephone$PaymentMethod)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)

p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Payment Method")+ylab("Percentage")
h<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

cowplot::plot_grid(a, b,c,d,e,f,g,h,ncol = 3)
```


```{r}
knitr::opts_chunk$set(echo = TRUE,fig.width = 8,fig.height = 5.5)
```

```{r}
a<-Telephone %>%
  group_by(Churn) %>%
  ggplot()+
  geom_boxplot(aes(x=Churn,y=tenure,fill="coral"))+
  guides(fill=FALSE)

b<-Telephone %>%
  group_by(Churn) %>%
  ggplot()+
  geom_boxplot(aes(x=Churn,y=MonthlyCharges,fill="coral"))+
  guides(fill=FALSE)

c<-Telephone %>%
  group_by(Churn) %>%
  ggplot()+
  geom_boxplot(aes(x=Churn,y=TotalCharges,fill="coral"))+
  guides(fill=FALSE)

cowplot::plot_grid(a, b,c,ncol = 3)      
```

```{r}
numerics=Telephone[c('tenure','MonthlyCharges','TotalCharges')]
correlations=cor(numerics)
corrplot(correlations,method = "number",type="upper")
```


## Separating Data sets into training and test - Telephone only
```{r}
set.seed(1024)
trainIndex <- sample(1:nrow(Telephone), size=round(0.75*nrow(Telephone)), replace=FALSE)
train <- Telephone[trainIndex,]
test  <- Telephone[-trainIndex,]
dim(train); dim(test)
summary(train)
```

## Creating the model - Telephone only
```{r}
reg2  <- glm(Churn ~SeniorCitizen+ Partner+ Dependents + MultipleLines + Contract + PaperlessBilling+PaymentMethod+tenure,family=binomial (link="logit"),data=train)
summary(reg2)
```

```{r}
vif(reg2)
dwtest(reg2)
```

## Calculating Accuracy, Precision, Recall and F-1 Score
```{r}
test_x <- test[ , c(1:12)]
predlogit <-predict(reg2, newdata=test_x, type="response")
predlogit <- ifelse(predlogit>0.19, 1, 0)

ConfusionMatrix<-table(test$Churn, predlogit) # Confusion matrix
ConfusionMatrix
ClassificationError <- mean(predlogit != test$Churn) # Classification error

pr <- prediction(predlogit, test$Churn)
prf <- performance(pr, measure="tpr", x.measure="fpr")
plot(prf)                                                 # ROC plot: TPR vs FPR

auc <- performance(pr, measure="auc")
auc <- auc@y.values[[1]]

TP = ConfusionMatrix[2,2]
TN = ConfusionMatrix[1,1]
FP = ConfusionMatrix[1,2]
FN = ConfusionMatrix[2,1]

precision<- round(TP / (TP + FP), 2)
recall<- round(TP / (TP + FN), 2)
f1_score<- round((2 * precision * recall) / (precision + recall), 2)

print(paste("Accuracy = ", 1-ClassificationError))
print(paste("AUC = ", auc))
print(paste("Precision = ", precision))
print(paste("Recall = ", recall))
print(paste("F-1 Score = ", f1_score))

```

```{r}
knitr::opts_chunk$set(echo = TRUE,fig.width = 12,fig.height = 15)
```

## Visualizing predictors with churn possibility - Internet only
```{r}
df2<-table(Internet$Churn,Internet$gender)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Gender")+ylab("Percentage")
a<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Internet$Churn,Internet$Partner)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Partner")+ylab("Percentage")
b<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Internet$Churn,Internet$Dependents)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Dependents")+ylab("Percentage")
c<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Internet$Churn,Internet$SeniorCitizen)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Senior Citizen")+ylab("Percentage")
d<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))



df2<-table(Internet$Churn,Internet$OnlineSecurity)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Online Security")+ylab("Percentage")
f<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Internet$Churn,Internet$OnlineBackup)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Online Backup")+ylab("Percentage")
g<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Internet$Churn,Internet$DeviceProtection)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Device Protection")+ylab("Percentage")
h<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Internet$Churn,Internet$TechSupport)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Tech Support")+ylab("Percentage")
i<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Internet$Churn,Internet$StreamingTV)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Streaming TV")+ylab("Percentage")
j<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Internet$Churn,Internet$StreamingMovies)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Streaming Movies")+ylab("Percentage")
k<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Internet$Churn,Internet$Contract)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Contract")+ylab("Percentage")
l<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Internet$Churn,Internet$PaperlessBilling)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)


p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Paperless Billing")+ylab("Percentage")
m<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

df2<-table(Internet$Churn,Internet$PaymentMethod)
df2<-round(100*prop.table(df2),digits=0)
df2<-as.data.frame(df2)

p<-ggplot(df2, aes(Var2, Freq)) + geom_bar(aes(fill = Var1), stat = "identity", position = "dodge")+xlab("Payment Method")+ylab("Percentage")
e<-p+scale_fill_discrete(name = "Churn", labels = c("No", "Yes"))

cowplot::plot_grid(a, b,c,d,e,f,g,h,i,j,k,l,m,ncol = 3)
```

```{r}
knitr::opts_chunk$set(echo = TRUE,fig.width = 8,fig.height = 5.5)
```

```{r}
a<-Internet %>%
  group_by(Churn) %>%
  ggplot()+
  geom_boxplot(aes(x=Churn,y=tenure,fill="coral"))+
  guides(fill=FALSE)

b<-Internet %>%
  group_by(Churn) %>%
  ggplot()+
  geom_boxplot(aes(x=Churn,y=MonthlyCharges,fill="coral"))+
  guides(fill=FALSE)

c<-Internet %>%
  group_by(Churn) %>%
  ggplot()+
  geom_boxplot(aes(x=Churn,y=TotalCharges,fill="coral"))+
  guides(fill=FALSE)

cowplot::plot_grid(a, b,c,ncol = 3)
```

```{r}
numerics=Internet[c('tenure','MonthlyCharges','TotalCharges')]
correlations=cor(numerics)
corrplot(correlations,method = "number",type="upper")
```

## Separating Data sets into training and test - Internet only
```{r}
set.seed(1024)
trainIndex <- sample(1:nrow(Internet), size=round(0.75*nrow(Internet)), replace=FALSE)
train <- Internet[trainIndex,]
test  <- Internet[-trainIndex,]
dim(train); dim(test)
summary(train)
```
## Creating the model - Internet only
```{r}
reg3<- glm(Churn ~ Partner+ Dependents + SeniorCitizen + PaymentMethod + OnlineSecurity + OnlineBackup + DeviceProtection + TechSupport + Contract + PaperlessBilling+tenure+MonthlyCharges,family=binomial (link="logit"),data=train)
summary(reg3)
```

```{r}
vif(reg3)
dwtest(reg3)
```


```{r}
test_x <- test[ , c(1:17)]
predlogit <-predict(reg3, newdata=test_x, type="response")
predlogit <- ifelse(predlogit>0.35, 1, 0)

ConfusionMatrix<-table(test$Churn, predlogit) # Confusion matrix
ConfusionMatrix
ClassificationError <- mean(predlogit != test$Churn) # Classification error

pr <- prediction(predlogit, test$Churn)
prf <- performance(pr, measure="tpr", x.measure="fpr")
plot(prf)                                                 # ROC plot: TPR vs FPR

auc <- performance(pr, measure="auc")
auc <- auc@y.values[[1]]

TP = ConfusionMatrix[2,2]
TN = ConfusionMatrix[1,1]
FP = ConfusionMatrix[1,2]
FN = ConfusionMatrix[2,1]

precision<- round(TP / (TP + FP), 2)
recall<- round(TP / (TP + FN), 2)
f1_score<- round((2 * precision * recall) / (precision + recall), 2)

print(paste("Accuracy = ", 1-ClassificationError))
print(paste("AUC = ", auc))
print(paste("Precision = ", precision))
print(paste("Recall = ", recall))
print(paste("F-1 Score = ", f1_score))

```

```{r}
stargazer(reg1,reg2,reg3,type="text",align = TRUE,single.row=TRUE,digits=2,out = "regout.txt")
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```


```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

